% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper,8pt]{extarticle}

\usepackage{setspace}
\linespread{0.1}

\newlength{\wideitemsep}
\setlength{\wideitemsep}{.5\itemsep}
\addtolength{\wideitemsep}{-5pt}
\let\olditem\item
\renewcommand{\item}{\setlength{\itemsep}{\wideitemsep}\olditem}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{color}
\usepackage{multicol}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Yaliang Wang}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {robot, balance, locomotion},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={7.4in, 10in},
  left=0.5in,
  top=0.5in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
%\usepackage{sectsty}
\definecolor{Gray}{rgb}{0.55,0.55,0.55}
%\sectionfont{\rmfamily\bfseries\large\color{Gray}}
%\subsectionfont{\rmfamily\mdseries\small}
\usepackage{titlesec}
\titleformat*{\section}{\rmfamily\bfseries\large\color{Gray}}
\titleformat*{\subsection}{\rmfamily\mdseries\normalsize}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.2in}

\begin{minipage}{0.45\linewidth}
  925 Dempster Apt. 2W \\
  Evanston, IL, 60201 \\
  United States 
  
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & 1 (224) 420 - 2689 \\
    Email: & \href{mailto:yaliangwang2015@u.northwestern.edu}{yaliangwang2015@u.northwestern.edu} \\
    Website: & \href{http://yaliang-wang.tk}{http://yaliang-wang.tk} \\
  \end{tabular}
\end{minipage}


%\section*{Personal}
%
%\begin{itemize}
%\item Born on April 30, 1990. People's Republic of China Citizen.
%\end{itemize}

%\section*{Objectives}
%
%\begin{itemize}
%\item Humanoid Balance, Robot Learning, Mechanically Adjustable Compliant Design, Robotics.
%\end{itemize}

\section*{Education \noindent\hrulefill}
%\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}

\begin{itemize}
  \item[$\circ$] M.S. Computer Science, Northwestern University. 3.74/4.00. \hfill {\it 2014 - present}
  \item[$\circ$] B.E. Automation(Control), Zhejiang University. 3.67/4.00。 \hfill {\it 2009 - 2013}
\end{itemize}

\section*{Skills \noindent\hrulefill}
\begin{itemize}
	\item[$\circ$] Python, C++, Javascript, Latex, MATLAB, PHP, Linux, Academic Writing.
\end{itemize}

\section*{Projects \noindent\hrulefill}

\subsection*{\textbf{Researcher, Master Thesis}, Detection, Tracking and Classification of Particles and Bubbles in IV Bags. \hfill {\it December, 2014 - present}}
\begin{itemize}
	\item[$\circ$] Detection: covert the grayscale image which generated from optical flow into binary image with a threshold produced from the histogram to get separable patches.
	\item[$\circ$] Tracking: match the patches with prediction from Kalman filter based on cost of shape and distance.
	\item[$\circ$] Classification: classify the tracks in the IV Bags into Particles or Bubbles.
\end{itemize}

\subsection*{\textbf{Algorithm Designer \& Coder}, Recommendation System in Streaming Music Service,
\href{https://github.com/Yaliang/last.fm-recommender}{\color[rgb]{0.2, 0.7, 0.7} Github}, \href{http://smarturl.it/coolrecommender}{\color[rgb]{0.2, 0.7, 0.7} Project Page}, \href{http://yaliang.github.io/last.fm-recommender/Dashboard.html}{\color[rgb]{0.2, 0.7, 0.7} Live Demo}. \hfill {\it April, 2015 - June, 2015}}
\begin{itemize}
	\item[$\circ$] Developing a K-nearest-neighbor based artist recommender. Python is used for this project. 
	\item[$\circ$] Based on the listen history of the users and the tags information of the artist on Last.fm, the recommender predicts the most favorite on a testing user. The current accuracy reached over 30\%.
\end{itemize}

\subsection*{\textbf{Algorithm Implementor}, Handwritten Digit Recognition, \href{https://github.com/Yaliang/Handwritten}{\color[rgb]{0.2, 0.7, 0.7} Github}, \href{https://drive.google.com/file/d/0B0flKXz1pWAcb2RIVU5SbUd0dkU/view}{\color[rgb]{0.2, 0.7, 0.7} Video(3 mins)}. \hfill {\it December, 2014 - March, 2015}}
\begin{itemize}
	\item[$\circ$] Developed and implemented 2-Layer Neural Network with 1000 hidden neurons.
	\item[$\circ$] Final achieved accuracy: 96.73 \% on the MNIST Dataset.  \hspace{0.2in} 
\end{itemize}

\subsection*{\textbf{Group Member}, Course Projects in Networking. \hfill {\it December, 2014 - March, 2015}}
\begin{itemize}
	\item[$\circ$] Developed a Web client and server based on the Minet Stack.
	\item[$\circ$] Implement TCP module on Minet Stack. 
	\item[$\circ$] Implement distance-vector algorithm in the context of a simple routing simulator.
	\item[$\circ$] All works are finished in C++.
\end{itemize}

\subsection*{\textbf{Independent Study}, Reinforcement Learning in Bipedal Walking Simulation. \hfill {\it December, 2014 - March, 2015}}
\begin{itemize}
	\item[$\circ$] Produced a survey on employing reinforcement learning to achieve humanoid robot walking.
\end{itemize}

\subsection*{\textbf{Product Manager \& Developer}, Social Networking Application. \hfill {\it December, 2014 - present}}
\begin{itemize}
	\item[$\circ$] Building a Hybrid App driven on HTML5, jQuery, jQuery Mobile, NodeJS(using EXPRESS), PhoneGap\texttrademark Build, Parse.com \& Heroku.com.
	\item[$\circ$] The App offers event-based social network. Users can post their activities to meet participants and chat with them. More features are under developing.
	
\end{itemize}

\subsection*{\textbf{Tech Team Member \& Main Contributor}, Shh...note, an anonymous text app. \href{https://github.com/sabughnaim/AquaMPD}{\color[rgb]{0.2, 0.7, 0.7} Github},  \href{http://sabughnaim.github.io/AquaMPD/web/indexV4.html}{\color[rgb]{0.2, 0.7, 0.7} Live Demo}.\hfill {\it Octerber, 2014 - December, 2014}}
\begin{itemize}
	\item[$\circ$] Developed the front-end based on HTML5, CSS3, jQuery \& jQuery Mobile and the back-end on PHP(using Silex), PostgreSQL \& Google Voice Text API hosted by Heroku.com.
	\item[$\circ$] Client Team is from students at Master Program of Product Design and Development. Agile development methodology is practiced in this project.
\end{itemize}

\subsection*{\textbf{Researcher, Bachelor Thesis}, Balance Maintenance for Humanoid Robots Subjected to External Disturbance. \href{http://yaliang-wang.tk/publications/}{\color[rgb]{0.2, 0.7, 0.7} Publications}, \href{http://yaliang-wang.tk/icra2014-video/}{\color[rgb]{0.2, 0.7, 0.7} Demo}. \hfill {\it December, 2012 - June, 2014}}
\begin{itemize}
	\item[$\circ$] First author of the paper published at ICRA 2014, top 1 international conference in robotics.
\end{itemize}

\section*{Awards \noindent\hrulefill}

\begin{itemize}
  \item[$\circ$] Best Student Application Paper Award, IFAC ICONS 2013, {\it  2013}.
  \item[$\circ$] Zhejiang University 2013 Session Excellent Bachelor Thesis Award, Zhejiang University, {\it  2013}.
\end{itemize}

\section*{Publications \noindent\hrulefill}

\begin{itemize}
\item[$\circ$] \textbf{Yaliang Wang}, Rong Xiong, Qiuguo Zhu, and Jian Chu, 
  "Compliance Control for Standing Maintenance of Humanoid Robots under Unknown External Disturbances",
  {\it 2014 IEEE International Conference on Robotics and Automation (ICRA 2014)}, pp. 2297-2304
  Hong Kong, China, May 31 - June 5, 2014.
\item[$\circ$] \textbf{Yaliang Wang}, Qiuguo Zhu, Rong Xiong, and Jian Chu, 
  "Standing Balance Control for Position Control-Based Humanoid Robot",
  {\it 3rd IFAC International Conference on Intelligent Control and Automation Science (IFAC ICONS 2013)}, pp.429-436, Chengdu, China, September 2-4, 2013.
\item[$\circ$] Chao Li, Rong Xiong, Qiuguo Zhu, Jun Wu, \textbf{Yaliang Wang}, Yiming Huang, "Push recovery for the standing under-actuated bipedal robot using the hip strategy", {\it Journal of Zhejiang University-SCIENCE}, 2014.
\end{itemize}



\section*{Exchange Experience \noindent\hrulefill}

\begin{itemize}
  \item[$\circ$] Vancouver Summer Business Program, 
   SAUDER School of Business, The University of British Columbia, {\it  July, 2012 - August, 2012}.
\end{itemize}

%\section*{Skills}
%\begin{itemize}
% \item Proficient in Matlab.
% \item Familiar with C/C++, Java, VHDL, PASCAL
%\end{itemize}

%\bigskip



% Footer
%\begin{center}
%  \begin{footnotesize}
%    %Last updated: \today \\
%    %\href{\footerlink}{\texttt{\footerlink}}
%  \end{footnotesize}
%\end{center}

\end{document}
